% LaTeX resume using res.cls
\documentclass[11pt]{res-modified}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\usepackage[margin=0.65in]{geometry}
\setlength{\topmargin}{-0.8in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{6pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
%\lhead{\hspace*{-\sectionwidth}Sarine Babikian} % force lhead all the way left
%\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document
\usepackage[none]{hyphenat}
\usepackage{hyperref}
\usepackage{amsmath}
\urlstyle{rm}
\begin{document} 
\sloppy
\thispagestyle{empty} % this page does not have a header

% Center the name over the entire width of resume:
%\moveleft.5\hoffset\centerline{\large\bf SARINE BABIKIAN}
%\moveleft.5\hoffset\centerline{\large\bf SARINE BABIKIAN}
 \textbf{\Large SARINE BABIKIAN}\\
% Draw a horizontal line the whole width of resume:
% \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
% \moveleft.5\hoffset\centerline{254 South Madison Avenue, \#15}
Pasadena, CA\\
818-913-4168  \hfill \url{ http://sarinebabikian.com}\\
sarine.babikian@gmail.com \hfill \url{ http://linkedin.com/in/sbabikian}\\

 % Draw a horizontal line the whole width of resume:
 \vspace{-10pt}
\moveleft\hoffset\vbox{\hrule width\textwidth height 0.5pt}
\vspace{-20pt}
\begin{resume}

\section{WORK EXPERIENCE} 
\vspace{1mm}
{\bf Research Assistant}, \textit{University of Southern California, Los Angeles, CA} \hfill 2012 - present \\
\textit{Understanding the details of human movement patterns and their control in the nervous system.}
\begin{itemize}
\item Designed human data collection experiments to gather data from multiple sensors (EEG, EMG, load cells, accelerometers).
%\item Designed and set up human data collection experiments using electroencephalography (EEG), fingertip forces, accelerometers, electromyogram (EMG) and functional Magnetic Resonance Imaging (fMRI). 
%\item Recruited human subjects, organized and led data collection.
\item Implemented machine learning using linear discriminant analysis combined with common spatial patterns to show that brain activity is correlated with variability in movement details.
\item Implemented a linear mixed-effects model to demonstrate that the relationship between prediction and ground truth is statistically-significant, while taking into account participant-specific dependencies.  
\item Developed and demonstrated that a bistable mathematical model of brain connections can reliably reproduce experimentally observed variability in brain activity.
\item Performed nonlinear optimization to simulate minimum-energy muscle activation patterns in movement performance.
\item Communicated findings to different audiences and at national and international scientific conferences. 
\end{itemize}

{\bf Teaching Assistant}, \textit{University of Southern California, Los Angeles, CA} \hfill 2013
\begin{itemize}
\item Assisted in teaching and preparing class material for a graduate level course on neuromuscular systems.
\item Prepared and delivered lectures on simulations of differential equations and Matlab programming tutorials.
\item Led weekly office hours, supervised students in their semester-long projects, graded homework and exams.
\end{itemize}

{\bf Mechanical Engineering Consultant}, \textit{Pierre Dammous and Partners, Beirut, Lebanon} \hfill 2009 - 2011
\begin{itemize}
\item Designed heating, ventilation, and air-conditioning (HVAC) networks for residential, commercial, university, and hospital buildings in Lebanon and the Gulf region.
%\item Performed project schematic design evaluation for compliance with MEP work.
%\item Worked both individually and in teams and assigned tasks to finish projects by deadline.
\item Worked both individually and in teams; and led multiple projects from start to submission.
\end{itemize}

%{\bf Information Technology Assistant}, \textit{American University of Beirut, Lebanon} \hfill Oct 2007 - Jun 2009 
%\begin{itemize}
%\item Assisted faculty and students in computer hardware and software set up and maintenance.
%\item Organized and maintained records of acquired hardware and software. 
%\end{itemize}

\section{EDUCATION}
\vspace{1mm}
\textbf{Ph.D.}, Mechanical Engineering, \textit{University of Southern California, Los Angeles, CA}  \hfill 2017\\
%Dissertation: Coordination in multi-muscle systems: from control theory to cortex.
\textbf{M.S.}, Biomedical Engineering, \textit{University of Southern California, Los Angeles, CA} \hfill 2012\\
\textbf{B.Eng.}, Mechanical Engineering, \textit{American University of Beirut, Lebanon} \hfill 2009


\section{SKILLS}
\vspace{5mm}
\begin{itemize}
\item Data analysis, machine learning, statistics, optimization, mathematical modeling, signal processing
\item Lab: EEG, EMG, fMRI, EKG
\item Programming: Matlab, Python, R
\end{itemize}

\section{AWARDS AND HONORS}
\vspace{1mm}
{WiSE Travel Grant}, \textit{University of Southern California, Los Angeles, CA} \hfill 2015 - 2017 \\
{Dean's Award for Creative Achievement}, \textit{American University of Beirut, Lebanon} \hfill 2009 \\
{Dean's Honor List}, \textit{American University of Beirut, Lebanon} \hfill 2008 - 2009

\end{resume}
\end{document}

















